Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-01 schemes.tex
Changes in TSNC

\ac{TSNC} can be considered an extension to \ac{SRLNC}. The overall idea is
not only for the encoder to generate sparse coded packets, but also to
choose the sparsity of packets wiser. That is, as the decoder accomulates more
coded packets it becomes more and more likely that the next received
coded packet will be \ac{l.d.}.

The idea of \ac{TSNC} is therefore to gradually increase the coding density
as the decoderes \ac{DOF} increases. This enables TSNC to save a lot of
complexity particulary in the beginning of transmissions, but also to
tailor the coding delay. I.e. approximate the number of coded packets a
decoder needs to receive to decode a generation of $g$ packets. We call
this number the budget, $B$.

>>>>

\ac{TSNC} can be considered an extension to \ac{SRLNC}. The key idea is
not only for the encoder to generate sparse coded packets, but also to
modify the code density of the packets progressively as required. As a
decoder accomulates more coded packets, the probability that the next
received coded packet will be \ac{l.d.} increases.

Therefore, in \ac{TSNC}, a simple procedure for controlling this probability
is to gradually increase the coding density as the \ac{DOF} increases. This enables TSNC to save a lot of
complexity particulary in the beginning of transmissions, but also to
tailor the coding delay. I.e. approximate the number of coded packets a
decoder needs to receive to decode a generation of $g$ packets. We call
this number the budget, $B$.
